\documentclass{dissertation-edit}

%% Turn off page numbering for the propositions and make the margins on both
%% sides equal and symmetrical.
\geometry{twoside=false}
\pagestyle{empty}

\begin{document}

%% Specify the title and author of the thesis. This information will be used on
%% both the English and Dutch side and in the metadata of the final PDF.
\title[Fundamental studies and applications]{Josephson junctions in superconducting coplanar DC bias cavities}
\author{Felix Erik}{Schmidt}

\begin{center}

{\Large\titlefont\bfseries Propositions}

\bigskip

accompanying the dissertation

\bigskip

%% Print the title.
{\makeatletter
\titlestyle\bfseries\large\@title
\makeatother}

%% Print the optional subtitle.
{\makeatletter
\ifx\@subtitle\undefined\else
    \titlefont\titleshape\@subtitle
\fi
\makeatother}

\bigskip

by

\bigskip

%% Print the full name of the author.
\makeatletter
{\large\titlefont\bfseries\@firstname\ {\titleshape\@lastname}}
\makeatother

\end{center}

\bigskip
\bigskip

\begin{enumerate}

\item Incorporating graphene Josephson junctions in superconducting microwave circuits can lead to coherent gate-tunable devices (chapter 3).
%
\item Implementing DC access to a microwave cavity, in addition to revealing information inaccessible to only low or high-frequency measurements, be useful in revealing noise sources (chapters 4 and 5).
%
\item Josephson junctions in DC bias cavities are a competitive technology for current detection to kinetic inductance devices (chapter 5).
%
\item Academic research would benefit by permanent staff taking over tasks like programming and lab management from self-taught graduate students.
%
\item Instead of only submitting text and images, jupyter notebooks should be the preferred format of publications in the physical sciences.
%
\item Failure to openly publish raw data, measurement and analysis scripts and details on fabrication and measurement setup accompanying papers and theses slows down scientific research.
%
\item Device fabrication plays an equally important role in achieving scientific publications as simulations and theory.
%
\item A lack of closely followed standards and practices in research, as compared to in industry, hampers scientific progress.
%
\item The only way to significantly slow man-made climate change is a long-lasting global economic recession.
%
\item While the Dutch train system may be equipped for daily commute, it is not suited for long distance travel.

\end{enumerate}

\bigskip
\bigskip

%% Apart from the name and title of the supervisor, the following text is
%% dictated by the promotieregelement.
\begin{center}
These propositions are regarded as opposable and defendable, and have been approved as such by the promotor Prof. Dr. G.A. Steele.
\end{center}

\clearpage
{\selectlanguage{dutch}

\begin{center}

{\Large\titlefont\bfseries Stellingen}

\bigskip

behorende bij het proefschrift

\bigskip

%% Print the title.
{\makeatletter
\titlestyle\bfseries\large\@title
\makeatother}

%% Print the optional subtitle.
{\makeatletter
\ifx\@subtitle\undefined\else
    \titlefont\titleshape\@subtitle
\fi
\makeatother}

\bigskip

door

\bigskip

%% Print the full name of the author.
\makeatletter
{\large\titlefont\bfseries\@firstname\ {\titleshape\@lastname}}
\makeatother

\end{center}

\bigskip
\bigskip

\begin{enumerate}

\item Opname van grafeen Josephson-juncties in supergeleidende microgolfcircuits kan leiden tot coherente gate-tunable apparaten (hoofdstuk 3).
%
\item Het implementeren van DC-toegang tot een microgolfholte, naast het onthullen van informatie die ontoegankelijk is voor alleen laag- of hoogfrequente metingen, kan nuttig zijn bij het onthullen van ruisbronnen (hoofdstukken 4 en 5).
%
\item Josephson-juncties in DC-bias-holtes zijn een concurrerende technologie voor stroomdetectie naar kinetische inductantie-apparaten (hoofdstuk 5).
%
\item Academisch onderzoek zou baat hebben bij uitbestedingstaken zoals programmeren en laboratoriumbeheer aan vaste medewerkers, in plaats van autodidactische afgestudeerde studenten.
%
\item In plaats van alleen tekst en afbeeldingen in te dienen, zouden jupyter-notebooks het geprefereerde formaat van publicaties in de natuurwetenschappen moeten zijn.
%\\
\item Onderzoekers die niet alle onbewerkte gegevens, meet- en analysescripts publiceren, evenals fabricage- en meetopstellingsdetails die hun papers en scripties vergezellen, openlijk toegankelijk, vertragen wetenschappelijk onderzoek.
%
\item De fabricage van apparaten moet een even belangrijke rol spelen in publiceerbaar werk als simulaties en theorie.
%
\item Een gebrek aan nauwkeurig gevolgde normen en praktijken in onderzoek, in vergelijking met in de industrie, belemmert de wetenschappelijke vooruitgang.
%
\item De enige manier om de door de mens veroorzaakte klimaatverandering aanzienlijk te vertragen, is een langdurige wereldwijde economische recessie.
%
\item Hoewel het Nederlandse treinsysteem is uitgerust voor dagelijks woon-werkverkeer, is het niet geschikt voor lange afstanden.

\end{enumerate}

\bigskip
\bigskip

%% Apart from the name and title of the supervisor, the following text is
%% dictated by the promotieregelement.
\begin{center}
Deze stellingen worden opponeerbaar en verdedigbaar geacht en zijn als zodanig goedgekeurd door de promotor Prof. Dr. G.A. Steele.
\end{center}

}

\end{document}

