\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\label{acknowledgements}

\epigraph[0pt]{
    Going down, party time \\
    My friends are gonna be there too.
}{{\bfseries AC{\faBolt}DC}~\cite{ac/dcHighwayHell1979}}

Doing my PhD was by no means a one-man job.
%
Without the help, encouragement and support from countless people, this research would not have been possible.
%
The following people played a very important role in me traveling down this road.

I was lucky to have two promotors, both with a curiosity for modern physics, and always trying to modernize their research infrastructure.
%
\textbf{Gary}, you are a great motivator and not only found the right words of encouragement when things were not going as planned, especially in the beginning of my PhD, but also leaped into action to deal with \enquote{political issues}.
%
In addition to me being drawn to Canadians, your curiosity in many different fields of physics was what got me hooked to join your group.
%
Thank you for your support, especially for the encouraging words on starting a family and making it possible for me to work remotely.
%
Thank you also to \textbf{Anton}, my second promotor.
%
It was always very refreshing, and at times eye-opening, to get another PI's perspective on both science and work place procedures.
%
Keep \textit{Plotocop} going, I'm looking forward to its future generations.
%
I would also like to thank all independent members of the committee for taking the time to evaluate this dissertation and giving me feedback.

To the people of SteeleLab:
%
\texttt{Henlo} \texttt{fr13nd} \textbf{Mark}, my fellow graphene team member!
%
We had a good whirl at merging DC bias cavities with graphene and boron nitride flakes.
%
It was a great moment when we saw the first graphene resonance, and a sad one when you left for the far north.
%
Thank you for (among other things) introducing me to VR, surreal memes, and touring Manchester, Teddington, Villard-de-Lans and Helsinki.
%
I'm looking forward to many more instances of Orang and Meme man!
%
\textbf{Martijn}, thank you for teaching me sarcasm and saying no to my supervisor.
%
Sorry for not bringing back the bicycles, but then again you had the cleaning personnel take care of my samples.
%
Current events forbid me to nominate paranymphs, but rest assured I would have liked to return the favor.
%
\textbf{Marios}, I enjoy our conversations, especially during these crazy times, on all things PhD and family related.
%
\textbf{Mario}, a big thank you for teaching me the intricacies of circuit anharmonicity, and the collaboration on the current detection paper.
%
I'm glad our trip overseas turned out to be so much fun.
%
\textbf{Byoung-moo}, I'm glad you can finally harvest the crops of your super-ambitious project.
%
Good luck with finishing things up!
%
\textbf{Sarwan}, I loved our obstacle runs together.
%
Keep mastering the membranes, workouts and cooking, and best of luck for the future!
%
I know you have great support with \textbf{Adrián}, who introduced me to the (currently) best Pizza bakery in Delft.
%
Keep the flag of \texttt{stlab/utils} flying!
%
\textbf{Daniel}, thank you for teaching me about microwave and superconducting physics, and the continuous flow of elegant mathematical derivations.
%
You were a great roommate to have on the Casimir ski trip!
%
Also thank you to the other half of the QOMSIM team, \textbf{Inês}!
%
We had a great collaboration on the current detection, and I wish you two all the best for your future.
%
Fingers crossed you keep up the success!
%
\textbf{Jasper}, you still have your entire PhD roller coaster ahead of you.
%
Hold on tight, and it shall be a good ride.
%
\textbf{Hadi}, it was nice to have a second 2D materials researcher in the group.
%
Best of luck with your research on the other side of the road.
%
\textbf{Fatemeh}, good to see your measurements are running, good luck!

In addition to me investigating graphene Josephson junctions, there were two other people in SteeleLab who pursued rather exotic topics, out of the scope of the central group theme:
%
\textbf{Nikos}, from the first time talking to you during my interview I knew that we would get along quite well.
%
Thank you for letting me crash on your couch on my first day of work, the good times in Boston, NYC and our office.
%
I wish you and your family all the best for the future.
%
Thank you \textbf{Yıldız}, the Turkish lady, for an always open ear for troubles, and for trusting me with your challenges.
%
Good luck with the final sprint to the finish line!

I would also like to thank all Bachelor and Master students who I supervised for showing me what it takes to improve my supervision skills:
%
In alphabetical (and chronological!) order, \textbf{Artiom, Daniël, Eagan} and \textbf{Pieter}.

Over the years, I have made some great friends in other groups of the department of Quantum Nanoscience.
%
\textbf{Sabina} and \textbf{Maria}, thank you for the many nice coffee and lunch breaks.
%
Sabina, thank you for lending me your ladder, and congratulations again and good luck with your position as assistant professor!
%
Maria, I was lucky to have experienced your excellent cooking skills. 
%
Thank you for treating us to some real Moroccan food in terms of quality and quantity.
%
\textbf{Nandini}, I still remember talking to you about monolayer \ce{MoS2} at the stamping setup and working in the \enquote{Death Lab} on the fourth floor.
%
I am glad you were able to start again at \textit{QuTech}, and am looking forward to the next \textit{Macarena} dance at one of your house parties.
%
\textbf{Moritz}, I think we started interacting regularly when teaching QM1, but in addition to that, I also enjoyed us being cleanroom nerds and our conversations about our personal lives.
%
Thank you for taking over for me in the PhD council, and good luck together with \textbf{Rob} for the remainder of your project!
%
Rob, not only at work, but also at Krashna, I had a great time with you around.
%
Thank you for the proofreading!
%
\textbf{Claus}, eating ribs at \textit{Wijnhaven} was a fun event, we have to do it again in the future!
%
\textbf{Luigi}, you always managed to catch me off-guard when greeting me as \enquote{Mr. Felix}!
%
I will gladly remember our time together on the PhD council and the discussions on how to etch and sputter things in the cleanroom.
%
In addition, \textbf{Edouard}, \textbf{Martin}, \textbf{Andreas}, \textbf{Igor}, \textbf{Miguel}, \textbf{Rasa}, \textbf{Jérémie} and \textbf{Joeri}, good luck with your current and future research and I am looking forward to our next conversations, be it on scientific or other topics.

During my time at \textit{QN} I had the pleasure to share an office with great people from various places:
%
\textbf{Mari Carmen}, you and I almost started on the same day, in the same third-floor-hidden-away office and, as it turned out, were both well acquainted with Mark!
%
My move to D110 separated us, but I'm glad we have still kept in contact.
%
Fellow office mates of D110, \textbf{Lorenzo, Magda, Nikos, Su-Hyun, Marc} and \textbf{Jie}, thank you for the discussions on both scientific and other matters.


In the cleanroom, I was privileged to get to interact with some great lithography experts:
%
\textbf{David} and \textbf{Ale}, thank you both for advice and chats on completely different topics, and sharing some of the best tips and tricks to increase the process quality.
%
\textbf{James, Willemijn} and \textbf{Srijit}.
%
We were frenemies and internal competition from day One.
%
Even though things were not easy, I am glad we made it out okay.
%
The \textit{Kavli Nanolab} cleanroom itself would not be standing without the following people:
%
\textbf{Frank, Marc, Eugene, Pauline, Ewan, Marco vdK, Marco B, Charles, Anja, Arnold, Hozanna, Ron, Roel} and \textbf{Lodi}.
%
You not only keep things from blowing up, but also up and running, even though it sometimes is the Wild West in there.
%
It was an amazing experience to be able to work in probably one of the best equipped university cleanrooms worldwide.

I would like to extend a \enquote{Heel erg bedankt} to the support staff and technicians of \textit{Quantum Nanoscience}:
%
\textbf{Etty, Maria, Marijke, Erika} and \textbf{Heleen}.
%
Thank you for taking care of so many administrative requests, never freaking out about the messy receipts for reimbursements and the countless hours of solving Basware related quirks and bugs.
%
\textbf{Tino, Ronald} and \textbf{Tom}, you always kept things rolling and never got tired of our requests to building new setups or sample holders.
%
Thank you to the entire team at \textit{DEMO}, especially \textbf{Erik} and \textbf{Jack}, for support in electrical matters and building the IVVI modules.
%
Thank you also to the great technicians at \textit{QuTech}, in particular \textbf{Jason, Raymond, Raymond} and \textbf{Marijn}, for support regarding electronics, PCBs and low-pass and copper powder filters.
%
In addition, all PIs at \textit{QN} deserve to be mentioned as well for enabling a dynamic and modern work environment:
%
\textbf{Sonia, Simon, Toeno, Andrea, Sander, Herre, Yaroslav} and \textbf{Kobus}.
	
Many of my former colleagues at \textit{QN} have long left the department, but shall not be forgotten here.
%
\textbf{Ranko}, a big \enquote{Hvala} for introducing me to Krashna, singing along with me during all these years, your insight to Montenegro, and the constant reminders to have more fun in my life.
%
\textbf{Willeke}, I admire your brave switch to the industry, and it seems you made a great choice.
%
Singing and going on tour together are some of my best memories of my time in Delft. 
%
\textbf{João}, I enjoyed our chats in \textit{QN} and our brief time together at Krashna.
%
\textbf{Holger}, the first \textit{EP III} guy from Würzburg, your spot-on questions on induced superconductivity and the underlying physics in my experiments were always a great challenge, which forced me to think hard about what it was I was measuring.
%
Thank you for that, and the fun we had as a group in Boston and New York.
%
\textbf{Chris}, yet another dude from NRW in the flatlands.
%
Even though we didn't interact much during our shared time in Delft, I am glad we kept in touch now that we both moved back to Germany.
%
All the best to you and Jasmin.

As already hinted above, singing in the \textit{Delftse Studenten Muziek Gezelschap Krashna Musika} and especially the interactions with other choir members were a great balance to research.
%
Thank you to all the friends I have made there, particularly, \textbf{Alexey}, \textbf{Christina}, \textbf{Jaime}, \textbf{Luca}, \textbf{Ozan} and \textbf{Tommaso}.
%
I will try to make it to as many future concerts as I can, and I miss singing already.

\begin{otherlanguage*}{german}
Zu guter Letzt möchte ich mich noch ganz herzlich bei meiner Familie bedanken.
%
\textbf{Mama} und \textbf{Papa}, danke dass ihr mich immer unterstützt, sowohl finanziell als auch emotional, meine Umzüge mitmacht und mich besuchen kommt, egal wohin es mich verschlägt.
%
Ganz besonderer Dank gilt \textbf{Katrin} und \textbf{Felicitas}:
%
Katrin, die gemeinsamen Jahre zusammen in Würzburg haben uns stark gemacht für die Zeit in Delft und Breyell.
%
Schön, dass das jetzt ein Ende hat, und wir gemeinsam weitermachen können.
%
Danke für alles, du bist für mich die Beste und ich liebe dich!
%
Felicitas, du rückst alles nochmal in eine neue Perspektive und zeigst mir, was im Leben wirklich wichtig ist.
%
Schön, dass du bei uns bist!
\end{otherlanguage*}